---
title: "Among Us JGraph"
output: rmarkdown::github_document
---

## List of Diagrams

1) Comparison of Layouts
+ Default (Jgraph)
+ Default (Kamada Kawai)

2) Comparisons with and without vents
+ Default (Jgraph)
+ Imposter (Jgraph)

3) Understanding Sabotages
+ Default (Jgraph) | Sabotage Rooms are coloured
    ++ Rootnode: (a) Lights (b) Comms (c) O2 (d) Reactor
+ Default (Radial Tree) | Sabotage Rooms are coloured
+ Default (Kamada Kawai) | Sabotage Rooms are coloured

Clear 
```{r}
rm(list = ls())
```

Library
```{r include=FALSE}
library(xml2)
library(rvest)
library(tidyverse)  
library(stringr)   
library(lubridate)
library(data.table)
library(network)
library(sjmisc)
library(igraph)
connect = read.csv("Data/skeldmap.csv")

#Two Edge List - With Vents and Without Vents
withoutVents = connect %>% filter(vents == 0)
withVents = connect
```

## 1 Comparison of Layouts

### 1a Default (Jgraph)
```{r}
tiff(filename="Diagrams/1a default-jgraph.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g1 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g1,flip.y=TRUE,root= "Cafeteria")
#Edge Color
E(g1)$color[E(g1)$vents == 0] <- 'green'

#Node Color
index = grep("Hallway",V(g1)$name)
V(g1)$color<-"green"
V(g1)[index]$color<-"red"

#Plot
plot(g1, layout=l, vertex.size=3, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```

### 1b Default (KK)
```{r}
tiff(filename="Diagrams/1b default-kk.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g1 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g1,flip.y=TRUE,root= "Cafeteria")
#Edge Color
E(g1)$color[E(g1)$vents == 0] <- 'green'

#Node Color

#Node Color
index = grep("Hallway",V(g1)$name)
V(g1)$color<-"green"
V(g1)[index]$color<-"red"

#Plot
plot(g1, layout=layout_with_kk, vertex.size=3,  vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```


## 2 Comparisons with and without vents

### 2a Default (Jgraph)
```{r}
tiff(filename="Diagrams/2a default-jgraph.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g1 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g1,flip.y=TRUE,root= "Cafeteria")
#Edge Color
E(g1)$color[E(g1)$vents == 0] <- 'green'

#Node Color
index = grep("Hallway",V(g1)$name)
V(g1)$color<-"green"
V(g1)[index]$color<-"red"

#Plot
plot(g1, layout=l, vertex.size=3, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```

### 2b Imposter (Jgraph)
```{r}
tiff(filename="Diagrams/2b imposter-jgraph.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g2 <- graph_from_data_frame(d=withVents,directed = FALSE)
l = layout_as_tree(g2,flip.y=TRUE,root= "Cafeteria")
#Edge Color
E(g2)$color[E(g2)$vents == 0] <- 'green'
E(g2)$color[E(g2)$vents != 0] <- 'orange'
#Node Color
index = grep("Hallway",V(g2)$name)
V(g2)$color<-"green"
V(g2)[index]$color<-"red"
#Plot
plot(g2, layout=l, vertex.size=3, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```


## 3 Understanding Sabotages

### 3a Default (Jgraph) | Sabotage Rooms are coloured
3a1 Fix Lights; Root = Electrical
```{r, fig.width = 25, fig.length = 4, fig.asp = .62}

tiff(filename="Diagrams/3a1 default-jgraph_FixLights.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g0 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g0,flip.y=TRUE,root= "Electrical 2")
#Edge Color
E(g0)$color[E(g0)$vents == 0] <- 'green'
#Node Color
index = grep("Hallway",V(g0)$name)
V(g0)$color<-"green"

index = grep("Communications",V(g1)$name)
V(g0)[index]$color<-"red"
index = grep("Electrical 2",V(g1)$name)
V(g0)[index]$color<-"violetred"
index = grep("Reactor 2",V(g1)$name)
V(g0)[index]$color<-"Purple"
index = grep("O2",V(g1)$name)
V(g0)[index]$color<-"orange"

name_df = data.frame(V(g1)$name) %>%
  mutate(size=3 )

name_df[grep("Communications", name_df$V.g1..name),]$size = 5
name_df[grep("Electrical 2", name_df$V.g1..name),]$size = 5
name_df[grep("Reactor 2", name_df$V.g1..name),]$size = 5
name_df[grep("O2", name_df$V.g1..name),]$size = 5

node.size<-setNames(name_df$size,name_df$V.g1..name)

#Plot
plot(g0, layout=l, vertex.size=node.size, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```

3a2 Comms Sabotage; Root = Communications
```{r, fig.width = 25, fig.length = 4, fig.asp = .62}

tiff(filename="Diagrams/3a2 default-jgraph_CommsSabotage.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g0 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g0,flip.y=TRUE,root= "Communications")
#Edge Color
E(g0)$color[E(g0)$vents == 0] <- 'green'
#Node Color
index = grep("Hallway",V(g0)$name)
V(g0)$color<-"green"

index = grep("Communications",V(g1)$name)
V(g0)[index]$color<-"red"
index = grep("Electrical 2",V(g1)$name)
V(g0)[index]$color<-"violetred"
index = grep("Reactor 2",V(g1)$name)
V(g0)[index]$color<-"Purple"
index = grep("O2",V(g1)$name)
V(g0)[index]$color<-"orange"

name_df = data.frame(V(g1)$name) %>%
  mutate(size=3 )

name_df[grep("Communications", name_df$V.g1..name),]$size = 5
name_df[grep("Electrical 2", name_df$V.g1..name),]$size = 5
name_df[grep("Reactor 2", name_df$V.g1..name),]$size = 5
name_df[grep("O2", name_df$V.g1..name),]$size = 5

node.size<-setNames(name_df$size,name_df$V.g1..name)

#Plot
plot(g0, layout=l, vertex.size=node.size, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```

3a3 Oxygen Depletion; Root = O2
```{r, fig.width = 25, fig.length = 4, fig.asp = .62}

tiff(filename="Diagrams/3a3 default-jgraph_jgraph - OxygenDepletion.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g0 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g0,flip.y=TRUE,root= "O2")
#Edge Color
E(g0)$color[E(g0)$vents == 0] <- 'green'
#Node Color
index = grep("Hallway",V(g0)$name)
V(g0)$color<-"green"

index = grep("Communications",V(g1)$name)
V(g0)[index]$color<-"red"
index = grep("Electrical 2",V(g1)$name)
V(g0)[index]$color<-"violetred"
index = grep("Reactor 2",V(g1)$name)
V(g0)[index]$color<-"Purple"
index = grep("O2",V(g1)$name)
V(g0)[index]$color<-"orange"

name_df = data.frame(V(g1)$name) %>%
  mutate(size=3 )

name_df[grep("Communications", name_df$V.g1..name),]$size = 5
name_df[grep("Electrical 2", name_df$V.g1..name),]$size = 5
name_df[grep("Reactor 2", name_df$V.g1..name),]$size = 5
name_df[grep("O2", name_df$V.g1..name),]$size = 5

node.size<-setNames(name_df$size,name_df$V.g1..name)

#Plot
plot(g0, layout=l, vertex.size=node.size, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```

3a4 Reactor Meltdown; Root = Reactor2
```{r, fig.width = 25, fig.length = 4, fig.asp = .62}

tiff(filename="Diagrams/3a4 default-jgraph_ReactorMeltdown.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g0 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g0,flip.y=TRUE,root= "Reactor 2")
#Edge Color
E(g0)$color[E(g0)$vents == 0] <- 'green'
#Node Color
index = grep("Hallway",V(g0)$name)
V(g0)$color<-"green"


index = grep("Communications",V(g1)$name)
V(g0)[index]$color<-"red"
index = grep("Electrical 2",V(g1)$name)
V(g0)[index]$color<-"violetred"
index = grep("Reactor 2",V(g1)$name)
V(g0)[index]$color<-"Purple"
index = grep("O2",V(g1)$name)
V(g0)[index]$color<-"orange"

name_df = data.frame(V(g1)$name) %>%
  mutate(size=3 )

name_df[grep("Communications", name_df$V.g1..name),]$size = 5
name_df[grep("Electrical 2", name_df$V.g1..name),]$size = 5
name_df[grep("Reactor 2", name_df$V.g1..name),]$size = 5
name_df[grep("O2", name_df$V.g1..name),]$size = 5

node.size<-setNames(name_df$size,name_df$V.g1..name)

#Plot
plot(g0, layout=l, vertex.size=node.size, vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```


### 3b Default (Radial Tree) | Sabotage Rooms are coloured
```{r, fig.width = 25, fig.length = 4, fig.asp = .62}
tiff(filename="Diagrams/3b default-radialtree-sabotages.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g0 <- graph_from_data_frame(d=withoutVents,directed = FALSE)
l = layout_as_tree(g1,flip.y=TRUE,circular = TRUE, root= "Cafeteria")

#Edge Color
E(g0)$color[E(g0)$vents == 0] <- 'green'
#Node Color
index = grep("Hallway",V(g0)$name)
V(g0)$color<-"green"

index = grep("Cafeteria",V(g1)$name)
V(g0)[index]$color<-"black"
index = grep("Communications",V(g1)$name)
V(g0)[index]$color<-"red"
index = grep("Electrical 2",V(g1)$name)
V(g0)[index]$color<-"violetred"
index = grep("Reactor 2",V(g1)$name)
V(g0)[index]$color<-"Purple"
index = grep("O2",V(g1)$name)
V(g0)[index]$color<-"orange"

name_df = data.frame(V(g0)$name) %>%
  mutate(size=3)


name_df[grep("Cafeteria", name_df$V.g0..name),]$size = 5
name_df[grep("Communications", name_df$V.g0..name),]$size = 5
name_df[grep("Electrical 2", name_df$V.g0..name),]$size = 5
name_df[grep("Reactor 2", name_df$V.g0..name),]$size = 5
name_df[grep("O2", name_df$V.g0..name),]$size = 5

node.size<-setNames(name_df$size,name_df$V.g1..name)

#Plot
plot(g0, layout=l, vertex.size=node.size,  vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```


### 3c Default (Kamada Kawai) | Sabotage Rooms are coloured
```{r, fig.width = 25, fig.length = 4, fig.asp = .62}
tiff(filename="Diagrams/3c default-kk-sabotages.tiff", width=5, height=5, units="in",
     pointsize=4, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

g0 <- graph_from_data_frame(d=withoutVents,directed = FALSE)

#Edge Color
E(g0)$color[E(g0)$vents == 0] <- 'green'
#Node Color
index = grep("Hallway",V(g0)$name)
V(g0)$color<-"green"

index = grep("Cafeteria",V(g1)$name)
V(g0)[index]$color<-"black"
index = grep("Communications",V(g1)$name)
V(g0)[index]$color<-"red"
index = grep("Electrical 2",V(g1)$name)
V(g0)[index]$color<-"violetred"
index = grep("Reactor 2",V(g1)$name)
V(g0)[index]$color<-"Purple"
index = grep("O2",V(g1)$name)
V(g0)[index]$color<-"orange"

name_df = data.frame(V(g0)$name) %>%
  mutate(size=3)


name_df[grep("Cafeteria", name_df$V.g0..name),]$size = 5
name_df[grep("Communications", name_df$V.g0..name),]$size = 5
name_df[grep("Electrical 2", name_df$V.g0..name),]$size = 5
name_df[grep("Reactor 2", name_df$V.g0..name),]$size = 5
name_df[grep("O2", name_df$V.g0..name),]$size = 5

node.size<-setNames(name_df$size,name_df$V.g1..name)

#Plot
plot(g0, layout=layout_with_kk, vertex.size=node.size,  vertex.label.family="", vertex.label.dist=0.7, vertex.label.degree=90)

dev.off()
```



#### How many topological steps does the Vent Save?
```{r}
library(rsppfp)

Vents = withVents %>% filter(vents !=0)%>% select(-one_of(c("weight")))%>% select(-one_of(c("directed")))

for (i in 1: nrow(Vents)){
  Vents$steps[i] = shortest.paths(g1, paste(Vents$source[i]), paste(Vents$target[i]) )[1]
}
Vents
```

```{r}
tiff(filename="Diagrams/steps-saved-from-each-vent.tiff", width=5, height=5, units="in",
     pointsize=10, compression="lzw", bg="white", res=1200,
     restoreConsole=TRUE)

Steps_Saved = Vents[3:4]$steps
hist(Steps_Saved)
#ggplot(DF, aes(x=vents,y=steps) ) + geom_point(shape=1,size=4) 

dev.off()
```
